Project Protocol

### 2019-10-21 protocol.Rmd
statistical analysis

The results will be analysed using a generalised linear model, with a subject random effect. There will be two main effects: plot type and trend model.

Each lineup has the same hypotheses:
$H_0:$ there is no real structure visible in the data plot
$H_1:$ there is real structure visible in the data plot

Each lineup is a set of m = 12 plots.
One plot contains data with a real structure.
The probability that an observer picks the data plot when it is really *not* different from the 11 null plots, is $1/m = 1/12$.

If a participant is able to identify the data plot from the lineup, we reject the null hypothesis.
Type I error rate, $\alpha$, is set to a level of $1/m = 1/12 = 0.083$.

Compare the percentage of times users select the real data in a lineup for the same set of data presented in choropleth maps and hexagon tile maps.
Compare percentages of correct responses $\hat{\pi}_C$ and $\hat{\pi}_H$:

Where $C$ denotes the use of choropleth maps and $H$ denotes the use of hexagon tile maps.

The percentage of correct responses where the respondent identified the real data in a choropleth map is denoted by $\hat{\pi}_C = (x_C +1)/(n_{100} + 1)$, similarly for hexagon tile maps: $\hat{\pi}_H = (x_H +1)/(n_{100} + 1)$.

@@

## Response variables

### Accuracy

@@

### Efficiency

@@

## Model

A multilevel linear model with be fitted to the data with elements as specified below.

Response Variables:
Accuracy and Efficiency

Main Effects:
Design, Trend

Random Effects:
The collection of multiple responses from each person as they complete several different lineup tasks, allows estimates of their perceptual ability using a subject-specific random intercept in a generalized linear model.

Possible Interactions:
Design and Trend, Design and Difficulty, Design and Reason

Possible covariates:
Responses to the questions regarding the difficulty of making a choice and the reason for the choice of plot in the line up.

@@

@@

#	Appendices 
 - These may include surveys, questionnaires, interview schedules, recruitment materials, manual of operations, etc

>>>>

@@

## Accuracy

@@

## Efficiency

@@

### Graphical analysis

For each lineup we will compute

- accuracy: the proportion of subjects who detected the data plot
- efficiency: average time taken to respond

Side-by-side dot plots will be made of accuracy (efficiency) against plot type, facetted by trend model type.

Similar plots will be made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.

Plots will be made in R~[@RCore], with the `ggplot2` package~[@ggplot2].

### Modeling

The results will be analysed using a generalised linear model, with a subject random effect. There will be two main effects: plot type and trend model, which gives the fixed effects part of the model to be

$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3$$

where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the plot type effect, $\delta_j$ is the trend model effect. We are allowing for an interaction between plot type and trend model. Because the response is binary, a logistic model is used.

A similar model will be constructed for the efficiency, using a log time, and normal errors.

The feedback and demographic variables will possibly be incorporated as covariates.

Computation will be done using R~[@RCore], with the `lme4` package~[@lme4].

@@

#	Appendices

A document on the web app is attached.

@@
